\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-04-29 JSS/jss-style/article.tex
switch dots to labels; add animate variable

The text labels are so numerous in Figure \ref{fig:plotCBText} that simply trying different values for the input parameter \code{binVector} will not solve the text overlapping problem. Instead, one approach we can try is to reconstruct the plot using the same \pkg{ggenealogy} function \code{plotPathOnAll()}, only now specifying variables to render the size (2.5) and color (default of black) of the text for nodes that are on the path of interest to be more noticeable than the size (0.5) and color (dark gray) of the text for nodes thare not on the path of interest. Moreover, we can make the edges that are not on the path of interest to be represented in a less noticeable color (light gray) than the edges that are on the path of interest (default of black). The variable names and options for these aesthetics is further detailed in the help manual of the function. We provide one example code that alters the defaults of the text color and sizes of nodes and edges below, which results in Figure \ref{fig:plotCBNoText}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{plotCBNoText}
    \caption{The shortest path between Sir David Cox and Petra Buzkova, superimposed over the data structure, using a bin size of 200. Individuals on the shortest path have text labels; all other individuals have dot labels.}
    \label{fig:plotCBNoText}
\end{figure}

@@

>>>>

The text labels are so numerous in Figure \ref{fig:plotCBText} that simply trying different values for the input parameter \code{binVector} will not solve the text overlapping problem. Instead, one approach we can try is to reconstruct the plot using the same \pkg{ggenealogy} function \code{plotPathOnAll()}, only now specifying variables to render the size (2.5) and color (default of black) of the text for nodes that are on the path of interest to be more noticeable than the size (0.5) and color (dark gray) of the text for nodes thare not on the path of interest. Moreover, we can make the edges that are not on the path of interest to be represented in a less noticeable color (light gray) than the edges that are on the path of interest (default of dark green). The variable names and options for these aesthetics is further detailed in the help manual of the function. We provide one example code that alters the defaults of the text color and sizes of nodes and edges below, which results in Figure \ref{fig:plotCBNoText}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{plotCBNoText}
    \caption{The shortest path between Sir David Cox and Petra Buzkova, superimposed over the data structure, using a bin size of 200. Individuals on the shortest path are labeled in large and black text and connected by dark green edges; all other individuals are labeled in small and gray text and connected by light gray edges.}
    \label{fig:plotCBNoText}
\end{figure}

@@

We could still improve upon Figure \ref{fig:plotCBNoText}. Even though we may be primarily interested in understanding how the path of interest is overlaid across the entire genealogical structure, we could, upon viewing the entire structure, also develop an interest in nodes that are not on the path of interest but are revealed to stand out among the rest of the genealogical structure. For instance, in Figure \ref{fig:plotCBNoText}, it may be of interest for us to determine the names of the few individuals who obtained their statistics degrees before 1900. Fortunately, within the \code{plotPathOnAll()} function, there is a variable \code{animate} that we can set to a value of TRUE to create an interactive version of the figure that allows us to hover over individual illegible labels and immediately receive their labels in a readable format.

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5,
   pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate =
   TRUE)
\end{CodeInput}
\end{CodeChunk}
